Synthesizing by means of mice with partially synthetic data rules

### 2021-01-18 mice_synthesizing/mice_updates.Rmd

---
title: "Mice udpates for synthetic data"
author: "Thom Volker"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "apa-6th-edition.csl"
---

>>>>

---
title: "Mice updates for synthetic data"
author: "Thom Volker"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "apa-6th-edition.csl"
---

### 2021-01-18 mice_synthesizing/synthesizing_partially_synthetic_data_rules.Rmd

```{r, results=FALSE, message=FALSE, warning=FALSE}
source("functions.R")
library(mice)
library(magrittr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggplot2)
```

```{r, include = FALSE}
load("~/Documents/Federated_imputation/mice_synthesizing/Mice_Synthesizing_cache/html/unnamed-chunk-1_3934488913d24a2b94b74c88c35323d4.RData")
```

>>>>

```{r, results=FALSE, message=FALSE, warning=FALSE}
source("simulations/functions.R")
library(mice)
library(magrittr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggplot2)
```

```{r, include = FALSE}
load("Mice_Synthesizing_cache/html/unnamed-chunk-1_3934488913d24a2b94b74c88c35323d4.RData")
```
